Visit Scotland Notebook

### 2023-06-17 visit_scotland_notebook.Rmd
Updated Visualisation Aesthetics / Added Template for README.md

### Annual Average Boxplots

```{r}
regional_domestic_tourism_all %>% 
  ggplot(aes(x = visits, y = region_of_residence)) +
  geom_boxplot(fill = "#540453", alpha = 0.5) +
  stat_summary(fun.y = mean, geom = "point", shape = 4, size = 5, color = "#1d1d65", fill="#1d1d65") +
  labs(
    title = "Distribution of Annual Number of Domestic Vistors",
    x = "Visits (Thousands)",
    y = "Region of Residence",
    subtitle = "3 Year Averages")
```

```{r}
regional_domestic_tourism_all %>% 
  ggplot(aes(x = expenditure, y = region_of_residence)) +
  geom_boxplot(fill = "#1d1d65", alpha = 0.5) +
  stat_summary(fun.y = mean, geom = "point", shape = 4, size = 5, color="#540453", fill="#540453") +
  labs(
    title = "Distribution of Average Annual Expenditure of Domestic Vistors",
    x = "Expenditure (Million GBP)",
    y = "Region of Residence",
    subtitle = "3 Year Averages")
```

@@

```
### Domestic Tourism / Nights Stayed

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = nights)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Nights (Thousands) \n",
       title = "Average Annual Nights Stayed by Domestic Vistors",
       subtitle = "3 Year Average")

@@

### Domestic Tourism / Expenditure per Visit

```{r}
regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = exp_per_visit)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "3x Year Average Expenditure per Visit (Thousands) \n",
       title = "Average Expenditure Per Visit Domestic Vistors",
       subtitle = "3 Year Average")
```

@@

>>>>

@@

@@

@@

#### Gross Value Added

```{r}
tourism_businesses %>%
  filter(local_authority != "Scotland",
         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  group_by(local_authority) %>% 
  summarise(total_gva = sum(gva)) %>% 
  slice_max(total_gva, n = 5)

tourism_businesses %>%
  filter(local_authority %in% c("City of Edinburgh", "Glasgow City", "Aberdeen City",
                                "Highland", "Fife"),
         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  ggplot() +
  geom_boxplot(aes(x = gva, y = local_authority, fill = local_authority), 
               alpha = 0.8,
               show.legend = FALSE) +
  scale_fill_manual(values = c("#540453", "#970061", "#1d1d65", "#b6cb2b", "#9fd6f3")) +
  scale_colour_manual(values = c("#540453", "#970061", "#1d1d65", "#b6cb2b", "#9fd6f3")) +
  labs(
    x = "Gross Value Added (Million GBP)",
    y = "Local Authority",
    title = "Distribution of Annual Gross Value Added",
    subtitle = "Top 5 Regions: 2009-2019"
  )
```
